Propositions as Sessions, Mechanically

### 2015-04-22 paper/presentation.tex
Working on comparing CP typing rules (informal vs. formal).

\begin{frame}
another frame for cp this time its well typing time
\end{frame}

\begin{comment}
lets take a look at cp's typing rules. here we used a well typed relation on
the process terms of cp. we require additional assumptions for environment
ordering and
\end{comment}

>>>>

\defverbatim\cprule{
\begin{coq}
Inductive cp_rule : proc -> penv -> Prop :=
  | $\cdots$
  | cp_cut :
      forall (L:atoms) P Q A $\Gamma$ $\Delta$P $\Delta$Q
             (PER: Permutation $\Gamma$ ($\Delta$P ++ $\Delta$Q))
             (CPP: forall (x:atom) (NL: x $\notin$ L),
                     (open_proc P x) $\tpcp$ (x $\sim$ A) ++ $\Delta$P)
             (CPQ: forall (x:atom) (NL: x $\notin$ L),
                (open_proc Q x) $\tpcp$ (x $\sim$ $\dualbt{A}$) ++ $\Delta$Q),
        $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$
  | $\cdots$
\end{coq}
}

\begin{frame}
\cprule
\end{frame}

\begin{comment}
lets take a look at cp's typing rules. here we used a well typed relation on
the process terms of cp. we require additional assumptions for environment
ordering and more attention is paid to the opening of subprocesses. this
presents the informal and formal definitions of cut.
\end{comment}
